Make any stupid plot you want

### 2021-01-25 draft/sections/math.tex
can has $S$

\subsubsection{Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a simple 2D opaque image $D=\mathbb{R}^5$ with a record $d \in D$ of the form
\begin{equation}
    d = (x, y, R, G, B)
\end{equation}
such that a graphic only has 2D position and color. To support overplotting and transparency, the fiber would be $D=R^{7}$ such that $d=(x,y,z, R, G, B, A)$,

%%define a region b = [top, bottom, right, left]
%% inverse of b is capital S_b

\subsubsection{Continuity of the Graphic $S$} 
\label{sec:graphic_base}
An assumption of graphical representations is that they match the continuity of the data, for example discrete data is mapped to discrete elements\cite{tufteVisualDisplayQuantitative2001,friendlyBriefHistoryData2008}, but the underlying topology $S$ of a graphic may need more dimensions than the data topology $K$ because of the specifications of the display space. Therefore we define the base space mapping from graphic $S$ to data $K$ 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}

 as the deformation retraction \cite{RetractionTopology2020} $\xi: S \rightarrow K$ that goes from a region $s \in S_{k}$ to its associated point $k$, such that when $\xi(s) = k$, $\xi^*\tau(s) = \tau(k)$.

\begin{figure}
    \includegraphics[width=1\textwidth]{figures/math/retraction_maps.png}
    \caption{The scatter and line graphic base spaces $S$ are larger than $K$ so that they can encode physical aspects of the glyph, such as shape (a circle) or thickness. The heatmap base $S$ is the same as $K$ because a heatmap is directly mapping the values in the data to the graphic.
    \note{add $\alpha, \beta$ coordinates}}
    \label{fig:graphic_retraction_map}
\end{figure}
Figure~\ref{fig:graphic_retraction_map} illustrates some examples of $\xi$. The base space $S$ is mapping to a in $D$. For example, in the scatter plot, $S$ encodes what the glyph looks like such that each piece of a single glyph maps to a different region on $S$. The line plot $S$ can encode position in the $\alpha$ dimension, but the $\beta$ dimension describes

The  line plot $S$ encodes on a plane  by necessity needs to have a thickness to be visible; therefore we construct a rectangular base space $S$ that mirrors the plane on which we can encode the position in one dimension and thickness (should this pixel be colored?) in the other. The map $xi$ then goes from a rectangle to

@@

>>>>

\subsubsection{Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a simple 2D opaque image $D=\mathbb{R}^5$ with a record $d \in D$ of the form
\begin{equation}
    d = (x, y, R, G, B)
\end{equation}
such that a graphic only has 2D position and color. To support overplotting and transparency, the fiber would be $D=R^{7}$ such that $d=(x,y,z, R, G, B, A)$. The location coordinates $x$ and $y$ are defined in terms of the display, while the \textrm{R,G,B} values are filled in via a lookup on $S$.

\subsubsection{Continuity of the Graphic $S$} 
\label{sec:graphic_base}
An assumption of graphical representations is that they match the continuity of the data\cite{tufteVisualDisplayQuantitative2001,friendlyBriefHistoryData2008}, but the underlying topology $S$ of a graphic may need more dimensions than the data topology $K$ so that the glyph can be defined in $D$. Therefore we define the base space mapping from graphic $S$ to data $K$ 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] & H \arrow[d, "\pi"'] \\
        K                   & S \arrow[l, "\xi"']
        \end{tikzcd}
\end{equation}

 as the deformation retraction \cite{RetractionTopology2020} $\xi: S \rightarrow K$ that goes from a region $s \in S_{k}$ to its associated point $k$, such that when $\xi(s) = k$, $\xi^*\tau(s) = \tau(k)$. While dimensions can be added to $S$, it retains the same continuity as $K$.

\begin{figure}
    \includegraphics[width=1\textwidth]{figures/math/retraction_maps.png}
    \caption{The scatter and line graphic base spaces $S$ are larger than $K$ so that they can encode physical aspects of the glyph, such as shape (a circle) or thickness. The heatmap base $S$ is the same as $K$ because a heatmap is directly mapping the values in the data to the graphic.
    \note{add $\alpha, \beta$ coordinates}}
    \label{fig:graphic_retraction_map}
\end{figure}

In figure~\ref{fig:graphic_retraction_map} each disk $S_k$ indexes how the records in $D$ are held together to generate a single glyph that is the visual representation of a single point in $F_k$. For the line, the region $\beta$ over a point $\alpha_i$ specifies the thickness of the line in $D$ for the corresponding section on the interval $K$. The heatmap has the same continuity in data space and graphic space such that no extra dimensions are needed.

@@

We define a section of the displayed graphic as a region on D defined by the bounding box $b=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]$
